---
title: "Novartis datathon"
date: "11/28/2020"
output: 
  powerpoint_presentation:
    default
  ioslides_presentation:
    widescreen: true
    logo: www/logo.png
    css: www/style.css
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F)
library(data.table)
library(ggplot2)
library(plotly)
ggplot2::theme_set(theme_dark())
dt <- fread("data/dt_merged.csv")
```

## NON-JUVENILE ASYMPTOTICS

- Team member EDUARD GIMENEZ
- Team member PATRICK ALTMEYER
- Team member SIMON NEUMEYER
- Team member JAKOB PÖRSCHMANN

## Overview

- Data exploration
- Methodology
- Forecasts
- Interpretation of results

# Data exploration

## Time series (normalized)

```{r}
dt_plot <- dt[,.(value=mean(vol_indexed,na.rm=T)),by=.(month_num,country)]
gg <- ggplot(dt_plot, aes(x=month_num, y=value, colour=country)) +
  geom_line() +
  scale_color_discrete(
    name="Country:"
  ) +
  labs(
    x="Month",
    y="Volumne (normalized)"
  )
ggplotly(gg)
```

## Country clusters

```{r}
months <- c(1,5,10,20)
dt_plot <- dt[,.(value=vol_indexed),by=.(month_num,brand,country)]
gg <- ggplot(dt_plot[month_num %in% months], aes(x=value, fill=country)) +
  geom_histogram(bins=50, position = "identity", alpha=0.5) +
  scale_fill_discrete(
    name="Country:"
  ) +
  facet_wrap(
    ~month_num
  ) +
  labs(
    x="Month",
    y="Count"
  )
ggplotly(gg)
```


## Existing observations

```{r}
ggplot(
  data=dt[month_num>-1,.(N=sum(!is.na(volume))),by=.(month_num,test)],
  aes(x=month_num, y=N)
) +
  geom_col(fill="coral", alpha=0.5) +
  facet_grid(
    cols = vars(test),
    scales = "free"
  ) +
  labs(
    x="Volume (normalized)",
    y="Count"
  )
```


# Methodology

## Framework

1. Fit `classifier.fit(X,y)` in parallel for all $m \in [1,24]$:

$$
\begin{aligned}
&&v_m&=\text{model}(\mathbf{X}_m) \\
\text{where}&& \mathbf{X}_m &= \begin{pmatrix}
\mathbf{C}_1 & v_{1,-137} & ... & v_{1,m-1} \\
... & ... & ... & ... \\
\mathbf{C}_{n_m} & v_{n_m,-137} & ... & v_{n_m,m-1}
\end{pmatrix}
\end{aligned}
$$

2. Predict `classifier.predict(X)` recursively for all $m \in [1,24]$ where

$$
\begin{aligned}
&& \mathbf{X}_m = \begin{pmatrix}
\mathbf{C}_1 & v_{1,-137} & ... & \hat{v}_{1,m-1} \\
... & ... & ... & ... \\
\mathbf{C}_{n_m} & v_{n_m,-137} & ... & \hat{v}_{n_m,m-1}
\end{pmatrix}
\end{aligned}
$$

## Confidence interval

- Normalised predictions are (largely) $\hat{\mathbf{v}}\in[0,1]$.
- We aim for small bands near 1 and 0 and wider bands elsewhere.
- Predictions can be thought of as being generated from a **beta distribution** with $\mathbb{E}(\mathbf{v})=\frac{\alpha}{\alpha+\beta}$
- Fix $\beta=5$ and compute $\alpha=\frac{\mathbf{v}\beta}{(1-\mathbf{v})}$ and then

```
L = sc.betaincinv(alpha, beta, .075)
U = sc.betaincinv(alpha, beta, .925)
```

## Beta distribution

![](www/beta.svg)

## Score function

PLACEHOLDER

# Forecasts

PLACEHOLDER

# Interpretation

PLACEHOLDER


